### 2022-07-21 src/text/1-introduction.tex
Further modifications

The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
as an open observatory in the domain. Its data will be shared
Thus there is a need for open analysis software as well.

Moreover, the operation of CTA as an observatory introduces the necessity of
sharing its data publicly. The data-reduction workflow of different IACTs of
the current generation is remarkably similar, resulting in a \textit{high} data
level that can be finally used to derive scientific results (, spectra, sky
maps, light curves). The information in this high data level is independent on
the data reduction, and eventually of the detection technique. This implies,
for example, that data from IACT and WCD can be represented within the same
model. The efforts to prototype the future CTA data model and to convert
current IACT data in a format usable with the newly-available science tools
converged in the so-called \textit{Data Format for Gamma-ray Astronomy}
initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
\texttt{gamma-astro-data-format} (GADF). The latter proposes prototypical
specifications to produce files based on the flexible image transport system
(FITS) format~\citep{fits} encapsulating this high-level information. This is
realized by storing a list of gamma-like events with their measured quantites
(energy, direction, arrival time) and a parametrisation of the response of the
system (see Sec.~\ref{ssec:gammapy-data} and Sec.~\ref{ssec:gammapy-irf} for
more information).

@@

% TODO: describe goals

@@

Here's a list of references I'd like to cite ... to be incorporated into the
main text somewhere:

\begin{itemize}
	\item Gammapy webpage\footnote{\GammapyUrl}
	\item Naima\footnote{\NaimaUrl}~\citep{Naima}
	\item Gammapy use in science publications:~\citep{Owen2015}, SNR shell, HGPS
\end{itemize}

* Gammapy – A Python package for gamma-ray astronomy
* Gammapy – A prototype for the CTA science tools
* Astropy: A community Python package for astronomy
* THE ASTROPY PROJECT: BUILDING AN INCLUSIVE, OPEN-SCIENCE PROJECT AND STATUS
OF THE V2.0 CORE PACKAGE * GammaLib and ctools * Fermipy proceedings * SunPy:
Python for Solar Physics. An implementation for local correlation tracking *

>>>>

Yet, the data-reduction workflow of different IACTs of the current generation is
remarkably similar. After data calibration, shower events are reconstructed and
gamma/hadron separation is applied to build lists of gamma-ray like events.
The latter are then used to derive scientific results, such as spectra, sky maps
or light curves, taking into account the Instrument Response Functions (IRF).
The information in this high data level is independent on
the data reduction, and eventually of the detection technique. This implies,
for example, that data from IACT and WCD can be represented within the same
model. The efforts to prototype a format usable by various instruments
converged in the so-called \textit{Data Format for Gamma-ray Astronomy}
initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
\texttt{gamma-astro-data-format} (GADF). The latter proposes prototypical
specifications to produce files based on the flexible image transport system
(FITS) format~\citep{fits} encapsulating this high-level information. This is
realized by storing a list of gamma-like events with their measured quantites
(energy, direction, arrival time) and a parametrisation of the response of the
system. (see Sec.~\ref{ssec:gammapy-data} and Sec.~\ref{ssec:gammapy-irf} for
more information).

The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
as an open observatory in the domain. Its high level data will be shared publicly after
some proprietary period and the software required to analyze it will be distributed
as well.

@@

% TODO: describe goals
The H.E.S.S. collaboration released a limited test dataset (about 50 hours of
observations taken between 2004 and 2008) based  on the GADF DL3 format \citep{HESS_DR1}.
This data release served as a basis for analysis tools validation \cite[see e.g.]{Mohrmann2019}.
% TODO : discuss joint crab paper?

@@
